Hierarchy Builder: algebraic~hierarchies made easy in Coq with Elpi

### 2020-04-29 hb.tex
refactoring concl + ack

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
In this paper we design and implement \HB{}, a high level language to describe
hierarchies of algebraic structures. The implementation of \HB{} is
based on the Elpi extension language for the Coq system and is available
at \url{https://github.com/math-comp/hierarchy-builder}.
The implementation amounts to approximately a thousand lines of (commented)
Elpi code and tree hundred lines of Coq vernacular. It took less than one month
to implement \HB{} while it took several years of attempts and fruitful
discussions with the other developers of the Mathematical Components library
to design it, as well as Coq users and developers and members of Dagstuhl seminar 18341.
In particular, discussions with Georges Gonthier, Assia Mahboubi and
Florent Hivert were instrumental in coining the concepts formalized here.

@@

We are particularly grateful to Georges Gonthier, Assia Mahboubi and
Florent Hivert for the many discussions we had that helped to shape
various parts of this work, as well as other developers of the
Mathematical Components library and members of Dagstuhl seminar
18341. We also thank many Coq developers and users who showed interest
and support in this work. We thank the anonymous reviewers of this
paper for their useful comments.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
In this paper we design and implement \HB{}, a high level language to describe
hierarchies of algebraic structures. The implementation of \HB{} is
based on the Elpi extension language for the Coq system and is available
at \url{https://github.com/math-comp/hierarchy-builder}.
The implementation amounts to approximately a thousand lines of (commented)
Elpi code and tree hundred lines of Coq vernacular. It took less than one month
to implement \HB{} but it took several years of attempts and fruitful
discussions with the people we thank below.

@@

We are particularly grateful to Georges Gonthier, Assia Mahboubi and
Florent Hivert for the many discussions we had that were instrumental
in coining the concepts formalized here. We thank as well other
developers of the Mathematical Components library and members of
Dagstuhl seminar 18341, for the helpful discussions we had. We also
thank many Coq developers and users who showed interest and support in
this work. Finally, we thank the anonymous reviewers of this paper for
their useful comments.
